My title

### 2024-11-27 paper/paper.qmd
fixed tables in paper.qmd

# TABLE 1: CLEANED DATASET
data %>% 
  head(5) %>%
  kable(booktabs = TRUE, linesep = "") %>%
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

@@

data %>% 
  select(-c(title)) %>% 
  summary(rated-high) %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)

>>>>

# TABLE 1: CLEANED DATASET
first_half <- data %>% select(1:6)

first_half %>% 
  head(5) %>%
  kable(booktabs = TRUE, linesep = "") %>%
  kable_styling(bootstrap_options = "condensed", full_width = FALSE)
```

```{r}
#| message: false
#| echo: false
#| warning: false

# CONTINUTATION OF TABLE 1: CLEANED DATASET
second_half <- data %>% select(7:12)

second_half %>% 
  head(5) %>%
  kable(booktabs = TRUE, linesep = "") %>%
  kable_styling(bootstrap_options = "condensed", full_width = FALSE)
```

@@

summary_table <- data %>%
  filter(!is.na(rated_high)) %>%  
  group_by(rated_high) %>%       
  summarise(
    avg_pages = mean(pages, na.rm = TRUE),          
    avg_publish_year = mean(publish_year, na.rm = TRUE),
    avg_rating_count = mean(rating_count, na.rm = TRUE)  
  )

summary_table %>% 
  kable(booktabs = TRUE, linesep = "") %>% 
  kable_styling(position = "left", bootstrap_options = "condensed", full_width = FALSE)
